Clean 2015 Raw Data

### 2017-08-24 data-raw/01-Clean_Raw_Data.Rmd
Add data-raw files

@@

save(DS2015, file = "../data/DS2015", compress = "bzip2")

@@

@@

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = as.vector(TShB_inc_15[1:5, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = as.vector(TShB_sev_15[1:5, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = as.vector(LShB_sev_15[1:5, 6]))

TShB_percent_AUDPS <-
  audps(evaluation = TShB_perc_wide[, 2:6],
        dates = as.vector(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  audps(evaluation = LShB_perc_wide[, 2:6],
        dates = as.vector(LShB_perc_15[1:5, 6]))

@@

ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")

@@

TShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  varrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = as.vector(TShB_inc_16[1:4, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = as.vector(TShB_sev_16[1:4, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = as.vector(LShB_sev_16[1:4, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = as.vector(TShB_perc_16[1:4, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = as.vector(LShB_perc_16[1:4, 6]))

@@

ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- tibble::as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- agricolae::mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

@@

save(AUDPS, file = "../data/AWD_AUDPS", compress = "bzip2")
```

>>>>

## 2015 raw data

@@

@@

## 2016 raw data

@@

## Calculate AUDPS and create final data for analysis

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = dplyr::pull(TShB_inc_15[1:5, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = dplyr::pull(TShB_sev_15[1:5, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
        dates = dplyr::pull(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
        dates = dplyr::pull(LShB_perc_15[1:5, 6]))

@@

ShB_15 <- dplyr::left_join(TShB_inc_15, AUDPS_15, by = "PLOT")

@@

TShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = dplyr::pull(TShB_inc_16[1:4, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = dplyr::pull(TShB_sev_16[1:4, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = dplyr::pull(LShB_sev_16[1:4, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = dplyr::pull(TShB_perc_16[1:4, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = dplyr::pull(LShB_perc_16[1:4, 6]))

@@

ShB_16 <- dplyr::left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- dplyr::mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

@@

save(AUDPS, file = "../data/AWD_AUDPS.rda", compress = "bzip2")
```
